---
title: "Aides Drug"
author: "Pedro Hernandez"
date: "05-04-19"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
avastFemale= filter(avast,sex=="F")
avastIV = filter(avast, Ivdrug== 'user')
avastLBGT = filter(avast, LBGT== 'yes')
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides (abacavirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation. 

The first question is this: does abacavirinol have any effect on whether one contracts AIDS or not?
abacavirinol has no effect on whether one contracts AIDS or not

abacavirinol has an effect on whether someone contracts AIDS or not

the remaining questions are: does abacavirinol have a different effect based on gender?

gender has no effect on whether abacavirinol offers protection against contracting AIDS

gender does have an effect on whether abacavirinol offers protection against contracting AIDS

sexual orientation has no effect on whether abacavirinol offers protection against contracting AIDS

sexual orientation does have an effect on whether abacavirinol offers protection against contracting AIDS

interveinous drug use has no effect
# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->
for each hypothesis test the graphical summary will be a bar plot. the numerical summary will be a cross tabulation, and a chi-squared test will be used for the inferetial results.

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->
Is the vaccine effective in the general population
## Descriptive Results
we use a bar chart to show the effectiveness of the vaccine on the general population

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->
```{r}
barchartGC(~infected+treatment, data=avast, type = 'percent')
```
the barchart shows that the general population is less likely to contract AIDs if they do take the vaccination.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward other people.-->

```{r}
genTable = xtabs(~infected+treatment, data = avast)
print(genTable)
```


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
chisq.test(genTable)
print(genTable)
```

The chi-squared test shows that the general population is less likely to contract AIDs if the vaccintation is taken

# Gender Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->
does abacavirinol have a different effect based on gender?
hypothesis: gender has no effect on whether abacavirinol offers protection against contracting AIDS

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->
for each hypothesis test the graphical summary will be a bar plot. the numerical summary will be a cross tabulation, and a chi-squared test will be used for the inferetial results.
#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->
Null hypothesis is that the vaccine has no effect on the general infected population focusing on specific genders. 
The p-value was  0 , so we reject the null hypothesis which is smaller than .05. Because the response and explanatory values are categorical, the bar plot and chi-squared test | test for independence.  


## Descriptive Results
we use a bar chart to show the effectiveness of the vaccine on the general population, allowing for gender

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->
```{r}
barchartGC(~sex+treatment, data=avast, type = 'percent')
```
with the data being shown on the barchart, there is no difference whether male or female benefit more from the vaccination.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
xtabs(~sex+treatment, data=avast)
```
with the data being shown on the cross tabulation, there is no difference whether male or female benefit more from the vaccination.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
chisqtestGC(~sex+treatment, data=avast)
```
with the data being shown on the chi-squared test, there is no difference whether male or female benefit more from the vaccination.

# Introduction for drug use

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->
does IV drug use have an effect on vaccine effectiveness.


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->
for each hypothesis test the graphical summary will be a bar plot. the numerical summary will be a cross tabulation, and a chi-squared test will be used for the inferetial results.
#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->
it is proven that drug users are more likely to be infected
## Descriptive Results
we use a bar chart to show the effectiveness of the vaccine on the general population, allowing for IV drug use

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->
```{r}
barchartGC(~infected+treatment, data=avastIV, type = 'percent')
```

the IV drug users are slightly more likely to get infected.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
xtabs(~infected+treatment, data=avastIV)
```
  
the cross tabulation shows that the IV drug users are more likely to get infected.
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
chisqtestGC(~infected+treatment, data=avastIV)
```

the chi-square test shows that IV drug users are more likely to get infected.

# Introduction FOR SEXUAL ORIENTATION

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->
does sexual orientation have an effect on vaccine effectiveness.


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->
for each hypothesis test the graphical summary will be a bar plot. the numerical summary will be a cross tabulation, and a chi-squared test will be used for the inferetial results.
#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->
IT IS PROVEN THAT THE VACCINE IS LESS EFFECTIVE FOR PROPLE OF THE LGBT COMMUNITY. 
## Descriptive Results
we use a bar chart to show the effectiveness of the vaccine on the general population, allowing for sexual orientation
### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->
```{r}
barchartGC(~infected+treatment, data=avastLBGT, type = 'percent')
```
according to the barchart the data shows that the vaccine is less effective for the LBGT community.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
xtabs(~infected+treatment, data=avastLBGT)
```
according to the cross tabulation and also the fisher test the data shows that the vaccine is less effective for the LBGT community.
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
LBGTtable=xtabs(~infected+treatment, data=avastLBGT)
fisher.test(LBGTtable)
```
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
Null hypothesis is that the vaccine has no effect on the general infected population.  

The p-value was  0 , so we reject the null hypothesis which is smaller than .05. Because the response and explanatory values are categorical, the bar plot and chi-squared test | test for independence.  

Based off of gender we fail to reject the null hypothesis. There was not a difference whether male or female took the vaccination

The null hypothesis shows that IV drug use had less effectiveness on the vaccination compared to the general population

the null hypothesis shows that based on the LBGT community the sexual orientation does not have any effect on the vaccination ratesof the population

Based on my final thoughts, the data shows that the vaccination may have some effect on the general population but there is not enough data to show for the other factors to completely reject the null hypotheses.

